Analyzing Housing Affordability in the United States: The Role of Inflation, Interest Rates, and Supply

### 2024-11-26 paper/paper.qmd
updated preambles and added final touches to the qmd file

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-cpi
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Consumer Price Index (CPI) Over Time'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-interest-rate
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Federal Funds Effective Interest Rate Over Time'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-housing-supply
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Housing Supply Over Time'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-growth-rates
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Growth Rates of House Prices and Wages'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-affordability-index
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Growth Rates of House Prices and Wages'

@@

# Additional data details

## Model Diagnostics {#sec-model-details}

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-diagnostic-plot
#| fig-cap: "Diagnostic Plots of Model 3 show that assumptions are largely met"
#| fig-width: 10
#| fig-height: 5

@@

## Idealized Methodology {#sec-ideal-meth}

### Limitations with FRED Methodology

@@

### Overview

@@

### Sampling Method

@@

### Recruitment Strategy

@@

### Data Validation

@@

### Conclusion

@@

### Section 1: Housing Situation

@@

### Section 2: Financial and Social Factors

@@

### Section 3: Perceptions of Housing Affordability

@@

### Section 4: Demographics

>>>>

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-cpi
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Trend in Consumer Price Index (CPI) from 2008 to 2024, highlighting a steady rise in inflation with accelerated growth post-2020.'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-interest-rate
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Historical trend of interest rates from 2008 to 2024, showcasing significant declines post-2008 financial crisis and sharp increases in recent years to combat inflation.'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-housing-supply
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Monthly housing supply trends from 2008 to 2024, highlighting peaks during the 2008 financial crisis and the COVID-19 pandemic, followed by declines as markets adjusted.'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-growth-rates
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Comparative growth rates of house prices and wages from 2006 to 2024, showing periods where house price increases significantly outpaced wage growth, particularly during housing market recoveries and economic expansions.'

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-affordability-index
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Trends in the Housing Affordability Index from 2006 to 2024, highlighting periods of increased affordability during economic downturns and decreased affordability during housing market peaks.'

@@

# Model Diagnostics {#sec-model-details}

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-diagnostic-plot
#| fig-cap: "Diagnostic Plots of Model 3 show that assumptions are largely met, with slight deviations"
#| fig-width: 10
#| fig-height: 5

@@

# Idealized Methodology {#sec-ideal-meth}

## Limitations with FRED Methodology

@@

@@

## Sampling Method

@@

## Recruitment Strategy

@@

## Data Validation

@@

## Conclusion

@@

Section 1: Housing Situation

@@

Section 2: Financial and Social Factors

@@

Section 3: Perceptions of Housing Affordability

@@

Section 4: Demographics
